Statistical Searches for Microlensing Events in Large, Non-Uniformly Sampled Time-Domain Surveys: A Test Using Palomar Transient Factory Data

### 2013-10-01 text/final_paper/ms.tex
added detail about delta chi squared and AIC BIC etc

We add one more index, $\Delta \chi^2$, the difference in $\chi^2$ between fitting a Gaussian model and fitting a linear model to a light curve. This is the standard statistical test used by microlensing surveys, and allows us to compare the relative performance of the (slightly modified) \cite{shin2009} indices and of this approach.

>>>>

We add one more index, $\Delta \chi^2$, the difference in $\chi^2$ between fitting a Gaussian model and fitting a linear model to a light curve. In detail, we use a Levenberg-Marquardt optimizer to perform a least-squares fit with each of these models to the light curves and then compute $\Delta\chi^2=\chi_{linear} - \chi_{gaussian}$. Out tests with $\Delta \chi^2$ below compare the distribution of values over light curves on the same chip --- because of this, we neglect including an AIC or BIC correction to make this a proper likelihood test as the number of data points and number of model parameters are constant. For the Gaussian fit, the optimizer is initialized with a standard-deviation of 10 days, centered on the brightest data point. This is the standard statistical test used by microlensing surveys, and allows us to compare the relative performance of the (slightly modified) \cite{shin2009} indices and of this approach.
